\section{Introduction} \label{sec:introduction}

Internet is a remarkable story. But the development of network is not done yet. 
The research of network is still on going. 
Partly it is because that network has achieved huge success in many different aspects, 
which makes modern enterprises heavily depend on it. 
As a result, more and more devices in enterprises are connected to the Internet, 
which makes the network larger and larger. Now as the network size keeps growing, 
we are facing some more challenging problems that are not considered when it is originally designed. 
One of those most challenging problems, and also what motived us to do this work is 
that the network behavior difference under different network topologies.

Let us first introduce the problem. 
Nowadays, many enterprises have more than one buildings 
which makes the devices connected to the Internet geographically distributed. 
But those networks will also share some common network equipments, 
like mail server or proxy server. 
Then how to design the network topology has became a critical problem. 
This problem is not only important for enterprises. 
It is also a very common problem we could possibly meet everyday. 
When we try to set up our own network in our houses or apartments. 
We are facing the same problem.

Different network topology will have a huge influence on the network behaviors. 
Among all the network features, two of them caught our attention: 
the overall throughput and fairness. 
First, we surely want to make full use of the network equipments we have. 
It will give us a better, faster and more reliable service 
if we can take advantage of the full power of the machines. 
And also, we want to treat each node in the topology equally, 
which means we need to guarantee fairness among all the nodes in the topology.
 
In this project, we will compare the network behaviors, 
focusing on overall throughput and fairness, under different topologies. 
And by studying this, we hope to answer the following question: 
What kind of topology is best for an enterprise when they try to design their network topology? 
We also believe that this work will also help families make decisions 
when they are arguing that how to deploy their home network.

Since the real network topology is very hard to simulate. 
We decide to simplify the problem a little bit. 
Firstly, we believe that the nodes in a topology will not be very large. 
This is a reasonable assumption, since devices within a certain distance 
could be logically merged into one node in the topology. 
Thus we decided to use seven nodes in our topology: 
one server node and six client nodes. This is another assumption we made. 
We decided to put the server nodes into only one logical node 
because in real world the servers shared by different departments are usually 
maintained by the IT department. And we also assume that 
the packet loss ratio is \textit{0.02}, which is considered acceptable \cite{PacketLoss:wiki}. 
Also to eliminate the influence of other factors like distance, 
we choose to use symmetric network topologies, 
and use the same distance between nodes and the same configuration for all the nodes.
Also, in our experiments, we choose to use TCP instead of other protocols since TCP is the most 
popular and widely used protocol in real world, which makes it very representative. Since we do not 
have real devices for us to do the experiments, we decided to use a famous network simulator called
Mininet\cite{Mininet:official} to simulate the topologies and collect data.

In the rest of the paper, we will go into details to talk about our experiments, and the analysis 
of our experiment results. The outline of the paper goes like this:
\begin{itemize}
    \item Section ``Approach'' will talk about the topologies we choose and why.
    \item Section ``Evaluation'' will have a discussion on the results of the experiments and our analysis.
    \item Section ``Summary'' will conclude our work including our limitations and introduce some related work. 
    Also we will try to mention some on going research challenges that is related to this topic.
\end{itemize}

